### 2013-09-03 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
whiitespace tweaks
fixing typo in nonlinear chapter

In addition to nonlinear iterative performance, performance of the
inner linear solves is also of interest. Here, we seek to minimize the
minimum number of total linear solver iterations over the course of
all nonlinear iterations in order to limit matrix-vector multiplies
and other costly
operations. Table~\ref{tab:convection_linear_iter_comparison} gives
the total number of GMRES, FANM, and Richardson iterations required to
converge the Newton method at each Rayleigh number used. For all
cases, fewer MCSA iterations were required than GMRES iterations to
converge the problem even with both solvers preconditioned with the
same multigrid package and the same parameters. For the \sn{1}{6}
Rayleigh number case where a constant forcing term of \sn{1}{-4} was
kept, this difference is most drastic with FANM requiring only 64\% of
the linear iterations required by the Newton-Krylov scheme with the
linear solver per nonlinear iteration given for this case in
Figure~\ref{fig:ra1e6_linear_iters}. Even the \sn{1}{5} Rayleigh
number case that required more Newton iterations required 5 fewer MCSA
iterations to converge than GMRES iterations. In all cases, MCSA
improved on the iterative performance of using only the Richardson
iteration through the residual Monte Carlo acceleration. If the
performance of the MCSA implementation used here were to be
potentially optimized in the future, this improved iterative
performance could also mean improved time to solution.

>>>>

In addition to nonlinear iterative performance, performance of the
inner linear solves is also of interest. Here, we seek to minimize the
minimum number of total linear solver iterations over the course of
all nonlinear iterations in order to limit matrix-vector multiplies
and other costly
operations. Table~\ref{tab:convection_linear_iter_comparison} gives
the total number of GMRES, MCSA, and Richardson iterations required to
converge the Newton method at each Rayleigh number used. For all
cases, fewer MCSA iterations were required than GMRES iterations to
converge the problem even with both solvers preconditioned with the
same multigrid package and the same parameters. For the \sn{1}{6}
Rayleigh number case where a constant forcing term of \sn{1}{-4} was
kept, this difference is most drastic with FANM requiring only 64\% of
the linear iterations required by the Newton-Krylov scheme with the
linear solver per nonlinear iteration given for this case in
Figure~\ref{fig:ra1e6_linear_iters}. Even the \sn{1}{5} Rayleigh
number case that required more Newton iterations required 5 fewer MCSA
iterations to converge than GMRES iterations. In all cases, MCSA
improved on the iterative performance of using only the Richardson
iteration through the residual Monte Carlo acceleration. If the
performance of the MCSA implementation used here were to be
potentially optimized in the future, this improved iterative
performance could also mean improved time to solution.
